\documentclass[10pt,a4paper,withhyper]{altacv}

\geometry{
left=1.25cm,
right=1.25cm,
top=1.2cm,
bottom=1.2cm,
columnsep=1.2cm
}

\usepackage{paracol}

\iftutex
\setmainfont{Roboto Slab}
\setsansfont{Lato}
\renewcommand{\familydefault}{\sfdefault}
\else
\usepackage[rm]{roboto}
\usepackage[defaultsans]{lato}
\renewcommand{\familydefault}{\sfdefault}
\fi

\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\definecolor{DarkPastelRed}{HTML}{450808}
\definecolor{PastelRed}{HTML}{8F0D0D}
\definecolor{GoldenEarth}{HTML}{E7D192}

\colorlet{name}{black}
\colorlet{tagline}{PastelRed}
\colorlet{heading}{DarkPastelRed}
\colorlet{headingrule}{GoldenEarth}
\colorlet{subheading}{PastelRed}
\colorlet{accent}{PastelRed}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

\renewcommand{\namefont}{\Huge\rmfamily\bfseries}
\renewcommand{\personalinfofont}{\footnotesize}
\renewcommand{\cvsectionfont}{\Large\rmfamily\bfseries}
\renewcommand{\cvsubsectionfont}{\large\bfseries}

\renewcommand{\cvItemMarker}{{\small\textbullet}}

\begin{document}

\name{Vishal Shrivastava}
\tagline{Founding Engineer | AI Systems Architect | Product Builder}

\personalinfo{
\email{[vishubth@gmail.com](mailto:vishubth@gmail.com)}
\location{Bangalore, India}
\linkedin{vishushri}
\github{vishubth}
}

\makecvheader

\columnratio{0.34}

\begin{paracol}{2}

\cvsection{Executive Summary}

Founding Engineer and AI Systems Architect with 6+ years of experience building AI platforms, fintech systems, data infrastructure, document intelligence solutions, cloud-native applications, and startup technology products.

Co-founded two startups, delivered 20+ projects across international markets, and led end-to-end product development from architecture and platform design through deployment and operational delivery.

Specialized in AI agents, RAG systems, MCP integrations, backend architecture, document intelligence, platform engineering, and enterprise automation.

\cvsection{AI Platform Portfolio}

\cvevent{Digital Asset Fundraising Operations Platform (NoGuy)}{}{}{}

\begin{itemize}
\item Architected investor onboarding, allocation management, transaction tracking, and blockchain payment verification workflows.
\item Designed layered FastAPI architecture using service, repository, and API orchestration patterns.
\item Built fintech operational tooling supporting digital asset fundraising and investor lifecycle management.
\end{itemize}

\divider

\cvevent{AI Document Intelligence Engine}{}{}{}

\begin{itemize}
\item Built OCR and LLM-powered document intelligence workflows.
\item Implemented extraction, chunking, schema validation, and profile generation pipelines.
\item Designed for compliance, onboarding, due diligence, and identity intelligence use cases.
\end{itemize}

\divider

\cvevent{AI Procurement Intelligence Platform}{}{}{}

\begin{itemize}
\item Building AI-native procurement intelligence and vendor evaluation platform.
\item Leveraging agentic workflows, retrieval systems, enterprise document processing, and workflow automation.
\item Designed around reusable AI infrastructure supporting future enterprise procurement operations.
\end{itemize}

\divider

\cvevent{ANC-VSNLMS Active Noise Cancellation Platform}{}{}{}

\begin{itemize}
\item Developed adaptive DSP platform implementing VSNLMS filtering.
\item Built real-time audio processing, benchmarking, and visualization pipelines.
\item Focused on low-latency signal processing and convergence optimization.
\end{itemize}

\cvsection{Professional Experience}

\cvevent
{Independent AI Consultant & Platform Engineer}
{International Clients}
{2020 -- Present}
{}

\begin{itemize}
\item Delivered AI, fintech, analytics, automation, and backend engineering solutions for international clients.
\item Built cloud-native platforms, APIs, data pipelines, and AI-powered applications.
\item Worked with startups and enterprise clients across US, UK, EU, AU, and Middle East markets.
\item Led architecture, implementation, deployment, and technical delivery across multiple engagements.
\end{itemize}

\divider

\cvevent
{Machine Learning Engineer}
{RadioCord Technologies}
{2024 -- 2025}
{}

\begin{itemize}
\item Developed voice recognition, speech-to-text, and audio intelligence systems.
\item Built AI-based noise cancellation algorithms and real-time audio processing pipelines.
\item Optimized model performance, latency, and inference efficiency.
\end{itemize}

\divider

\cvevent
{Co-Founder & Technical Lead}
{Futurova Technologies}
{2022 -- 2023}
{}

\begin{itemize}
\item Led development of IoT, telemetry, GPS tracking, and operational monitoring systems.
\item Built MQTT-based cloud integrations and dashboard platforms.
\item Drove product architecture and technical decision making.
\end{itemize}

\divider

\cvevent
{Co-Founder & Lead Developer}
{VegiBee}
{2021 -- 2022}
{}

\begin{itemize}
\item Developed AgriTech platform supporting supply-chain visibility and logistics optimization.
\item Built dashboards, analytics systems, and operational workflows.
\item Integrated technology solutions for agricultural operations and stakeholder management.
\end{itemize}

\switchcolumn

\cvsection{Career Highlights}

\cvachievement{\faTrophy}{6+ Years}{Software, AI and Platform Engineering}

\divider

\cvachievement{\faProjectDiagram}{20+ Projects}{Delivered Across Multiple Domains}

\divider

\cvachievement{\faGlobe}{International Experience}{US, UK, EU, AU and Middle East}

\divider

\cvachievement{\faRocket}{2 Startups}{Co-Founded and Built}

\cvsection{Core Expertise}

\cvtag{AI Agents}
\cvtag{RAG}
\cvtag{MCP}

\smallskip

\cvtag{Fine-Tuning}
\cvtag{Document Intelligence}
\cvtag{FastAPI}

\smallskip

\cvtag{System Design}
\cvtag{Data Engineering}
\cvtag{Cloud Architecture}

\smallskip

\cvtag{Microservices}
\cvtag{Platform Engineering}

\cvsection{Technology Stack}

Python

C/C++

JavaScript

\divider

FastAPI

Django

Flask

\divider

PostgreSQL

MySQL

MongoDB

Redis

\divider

AWS

GCP

Azure

Docker

Kubernetes

\divider

LLMs

RAG

Agents

OCR

NLP

\divider

Git

Linux

CI/CD

\cvsection{Education}

\cvevent
{Integrated MSc Mathematics}
{SVNIT}
{2014 -- 2020}
{}

Focus Areas:

Applied Mathematics

Computer Science Fundamentals

Algorithms

Problem Solving

Computational Thinking

\cvsection{Target Roles}

\cvtag{Founding Engineer}

\cvtag{AI Product Engineer}

\cvtag{AI Systems Architect}

\cvtag{Head of AI}

\cvtag{Technical Co-Founder}

\end{paracol}

\end{document}
